---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data
After cloning the [GitHub repository](http://github.com/rdpeng/RepData_PeerAssessment1) for this assignment. 

Reader should load the necesary libraries  

```{r load, echo=TRUE, message=FALSE, warning=FALSE}
library(dplyr)
library(lubridate)
library(ggplot2)
```

Set the working directory and unzipp the activity.zip file.  

Then read the csv file and change date format.  

```{r read, echo=TRUE, warning=FALSE}
setwd("~/RepData_PeerAssessment1")
unzip("activity.zip")
data<-read.csv("activity.csv")

```
## What is mean total number of steps taken per day?

1. Make a histogram of the total number of steps taken each day  

```{r calculate, echo=TRUE, warning=FALSE}
data %>% 
  tbl_df() %>% 
  mutate(date = as.Date(date)) %>% 
  group_by(day = floor_date(date, "day")) %>%
  summarise(total_steps = sum(steps)) %>% 
  ggplot(aes(x=total_steps)) + geom_histogram(color="black", fill="blue", binwidth = 5000)
```

Calculate and report the **mean** and **median** total number of steps taken per day  

```{r avg, echo=TRUE, warning=FALSE}
data %>% 
  tbl_df() %>% 
  mutate(date = as.Date(date)) %>% 
  group_by(day = floor_date(date, "day")) %>%
  summarise(total_steps = sum(steps)) %>% 
  summary() 
  
``` 
Mean   :10766

Median :10765

## What is the average daily activity pattern?

1. Make a time series plot (i.e. `type = "l"`) of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
